Simple simulations for a simplified version of web-boost-2

### 2020-05-28 analysis/index.Rmd
mr.ash2s

## Test veb_boost
A simplified version: interative update of two mr.ash components

@@

>>>>

## Test veb_boost
A simplified version (mr.ash2): interative update of two mr.ash components

@@

A simplified version (mr.ash2s): interative update of two mr.ash components, now including updates of sigma2 in each iteration and initiate with mr.ash for all.

  * [Using some simple data](simulation_simpleveb-boost2.html)

  * [Using UKbiobank data (chr22)](simulation-simpleveb-boost2-ukbchr22.html)

## Test SUSIE for fine-mapping

  * [Using some simple data](simulation_susie.html)

  * [Using UKbiobank data (chr22)](simulation-susie-ukbchr22.html)

### 2020-05-28 analysis/simulation_simpleveb-boost2.Rmd
mr.ash2s

---
title: "Simple simulations for a simplified version of web-boost"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mr.ash.alpha)
source("~/causalTWAS/causal-TWAS/code/fit_mr.ash.R")
source("~/causalTWAS/causal-TWAS/code/simple_vebboost.R")
```

@@

## Run a simplified version of veb-boost

@@

```{r run mr.ash2, gene}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2(X.gene, X.SNP, y)

@@

```{r run mr.ash2, snp}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2(X.SNP, X.gene, y)

>>>>

---
title: "Simple simulations for a simplified version of web-boost-2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mr.ash.alpha)
source("~/causalTWAS/causal-TWAS/code/fit_mr.ash.R")
source("~/causalTWAS/causal-TWAS/code/mr.ash2.R")
```

@@

## Run a simplified version of veb-boost (mr.ash2s)

@@

```{r run mr.ash2, gene}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2s(X.gene, X.SNP, y)

@@

```{r run mr.ash2, snp}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2s(X.SNP, X.gene, y)

### 2020-05-28 analysis/simulation_susie.Rmd
mr.ash2s

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mr.ash.alpha)
source("~/causalTWAS/causal-TWAS/code/fit_mr.ash.R")
source("~/causalTWAS/causal-TWAS/code/mr.ash2.R")
```

@@

## Run mr.ash

```{r plot functions}
summary_mr.ash <- function(fit){
  cat("pi1 = ", 1-fit$pi[[1]], "\n")
  pve <- get_pve(fit)
  cat("pve : ", pve, "\n")
}

plot_beta <- function(beta,beta.pm, ...){
  plot( beta, pch=19, col ="darkgreen", ...)
  points(beta.pm, pch =19, col = "red")
  legend("topright", legend=c("true beta", "posterior mean"),
       col=c("darkgreen", "red"), pch=19)
}

@@

```{r run mr.ash}
fit <- mr.ash(X, y, method="caisa")
summary_mr.ash(fit)

plot_beta(beta[gene.idx], fit$beta[gene.idx], main = "beta for gene effect")
plot_beta(beta[SNP.idx], fit$beta[SNP.idx], main = "beta for SNP effect")
```

## Run a simplified version of veb-boost (mr.ash2s)

### start with gene

```{r run mr.ash2, gene}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2s(X.gene, X.SNP, y)

print("for gene effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[gene.idx], fit$fit1$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[SNP.idx], fit$fit2$beta, main = "beta for SNP effect")
```

### start with SNP

```{r run mr.ash2, snp}
X.gene <- X[,gene.idx]
X.SNP <- X[, SNP.idx]
fit <- mr.ash2s(X.SNP, X.gene, y)

print("for gene effect: ")
summary_mr.ash(fit$fit2)
plot_beta(beta[gene.idx], fit$fit2$beta, main = "beta for gene effect")

print("for SNP effect: ")
summary_mr.ash(fit$fit1)
plot_beta(beta[SNP.idx], fit$fit1$beta, main = "beta for SNP effect")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(susieR)
```

@@

```{r plot functions}
plot_pip <- function(indi, pip, pipcut = 0.1) {
  x <- barplot(indi, main = "PIP")
  points(x, pip, pch=19, col="red")
  pred <- which(pip > pipcut)
  real <- which(indi==1)
  tp <- length(intersect(pred, real))/length(pred)
  fp <- 1 - tp
  fn <- length(setdiff(real, pred))/length(real)
  cat("false positive rate: ", fp, "\n")
  cat("false negative rate: ", fn, "\n")
}

@@

## Run susie

Fix prior as given, using truth.

```{r run susie, gene}
p.snp <- length(SNP.idx)
p.gene <- length(gene.idx)

prior.SNP <- 16/2000
prior.gene <- 4/20
indi.gene <- c(rep(1,4), rep(0,16))

prior <- rep(0, dim(X)[2])
prior[gene.idx] <- prior.gene
prior[SNP.idx] <- prior.SNP

res <- susie(X,y,L=1, prior_weights=prior)

print("for gene effect: ")
plot_pip(indi.gene, res$pip[gene.idx])
```
